\TitlePt

### 2016-03-18 conclusion.tex
Two paragraphs for the inversion method

>>>>

We used the tesseroid forward modeling and inverse problem toolkit of
\textit{Fatiando a Terra} to implement a new non-linear gravity inversion
method to estimate the depth of the Moho.
The inversion method uses the Gauss-Newton formulation of Bott's method
proposed by \citet{silva2014}.
In this formulation, the Jacobian (sensitivity) matrix is approximated by a
linear diagonal matrix.
This eliminates the high computational cost of calculating the full dense
Jacobian matrix for every iteration of the Gauss-Newton method.
We stabilize the inverse problem through smoothness regularization.
The use of regularization required that we abandon the elimination of linear
systems of the traditional Bott's method.
However, we maintained computational efficiency by taking advantage of the fact
that all matrices involved are sparse.
Our benchmarks suggest that less than 0.1\% of the computation time required
for an inversion is spent on matrix operations and solving linear systems.
We also estimate the regularization parameter and two other hyper-parameters of
the inversion through cross-validation procedures.

The applications to synthetic data show the
efficiency of the proposed inversion method in retrieving smooth Moho depth
variations.
The cross-validation procedures are able to correctly estimate an optimal
regularization parameter, anomalous Moho density-contrast, and the reference
level (the depth of the Normal Earth Moho).
We applied the proposed method to estimate the Moho depth of the South American
continent.
The estimated Moho depths are in agreement with previous models and with the
major tectonic provinces of the continent.
Notable misfits between the observed and predicted gravity data are in the
Andes, northern Venezuela, and the Paraná, Solimões, and Amazon Basins.
These regions also present a high misfit with Moho depth estimates from
seismology.
Discrepancies between gravity-derived and seismological estimates of Moho depth
may indicate the presence of other density anomalies with the crust or upper
mantle.
For example, \citet{mariani2013} and \citet{nunn1988} explain the discrepancies
in the Paraná and Amazon Basins, respectively, as high density material in the
lower crust.
